\bf\mftitle

### 2011-03-01 doc/jInfer/xsdimport/xsdimport.tex
xsdimport blueah

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & BasicIGG \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.xsdimporter.interfaces \\
                       & cz.cuni.mff.ksi.jinfer.xsdimporter.utils \\ \hline
\end{tabular}
\\

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & XSDImporter \\ \hline
Public packages:       & none \\ \hline
\end{tabular}
\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies   & Base \\ 
                       & BasicIGG \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.xsdimporter.interfaces} \\
                       & \code{cz.cuni.mff.ksi.jinfer.xsdimporter.utils} \\ \hline
\end{tabular}
\\

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies   & Base \\ 
                       & XSDImporter \\ \hline
Public packages       & none \\ \hline
\end{tabular}
\\
